A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-10-08 paper/ms.tex
update ms

\title{
  %Kepler 1627Ab: A 38 Million Year Old
  %Kepler 1627 Ab:
  %A Mini-Neptune in the Kepler Field Only 38 Million Years Old
  A 38 Million Year Old Mini-Neptune in the Kepler Field
}

@@

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.8\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\,{\rm pc}$) and it resembles the Sun.  Here we show
  using Gaia kinematics, TESS stellar rotation periods, and
  spectroscopic lithium abundances that Kepler\,1627 is a member of
  the \clusterage\ old $\delta$~Lyr cluster.  To our knowledge, this makes
  Kepler\,1627Ab the youngest planet with a precise age yet found
  by the main Kepler mission.
  The Kepler photometry shows two 
  peculiarities: the average transit profile is
  asymmetric, and the individual transit times are correlated with the
  local light curve slope.
  We discuss possible explanations for each anomaly.
  More broadly applicable though is the fact that the $\delta$~Lyr
  cluster is one of $\sim$10$^3$ clusters whose properties have been
  clarified by Gaia.  Many other exoplanet hosts are candidate
  kinematic members of these clusters; their cluster memberships can
  be verified by measuring stellar rotation periods in the TESS full
  frame images.
\end{abstract}

@@

%TODO: might want to revise this text to better frame the boil-off phase...
%TODO: better citations on radius evolution?
For instance, the ``mini-Neptunes'', thought to be made of molten
rocky cores \citep{kite_atmosphere_2020} and extended atmospheric
envelopes of hydrogen and helium, are expected to shrink in size by
factors of several over their first $10^8$ years.  Specifically, in
the models of \citet{owen_atmospheres_2016} and
\citet{owen_constraining_2020}, the $\approx5\,M_\oplus$ planets start
with sizes of 4--12\,$R_\oplus$ shortly after the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2--4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years after disk
dispersal \citep{owen_atmospheres_2016}, the combination of stellar
irradiation and internal heat may also power a more gradual outflow
which can eventually deplete or entirely strip the envelope from the
rocky core \citep{Owen_Wu_2013,ginzburg_corepowered_2018}.
Discovering young planets, measuring their masses, and detecting their
atmospheric outflows are key steps toward testing this paradigm, which
is often invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017}.

@@

Matching our young star list against stars observed by Kepler revealed that
%two discoveries.  The first, to be discussed in an upcoming analysis
%by J.~Curtis et al{.}, is that Kepler observed the $\approx$350\,Myr
%open cluster Theia~520 (UBC~1).  At least six Kepler planets are known
%in the cluster from the Kepler-52 and Kepler-968 systems
%\citep{rowe_validation_2014,jontof-hutter_following_2021}.  The second
%discovery, and the focus of this work, is
Kepler observed a portion of the \cn\ (Stephenson-1;
Theia~73).
More specifically, a clustering analysis of the Gaia
data by \citet{KounkelCovey2019}
reported that Kepler~1627 (KIC 6184894; KOI 5245; TIC 120105470) is a
\cn\ member.  Given the
previous statistical validation of the close-in mini-Neptune Kepler
1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by examining the properties of the cluster (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and 
in 
Section~\ref{sec:stars} show
that \sn\ is both a binary and also a member of the cluster.
Focusing on the planet (Section~\ref{sec:planet}), we confirm that despite the
existence of the previously unreported M2.5V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.  Based on a correlation between the
planetary transit times and the local light curve slope, the orbit
may also be prograde.  We conclude by highlighting broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

\citet{KounkelCovey2019} applied an unsupervised clustering
algorithm to Gaia DR2 on-sky positions, proper motions, and
parallaxes for stars within the nearest kiloparsec.  For the \cn\
(Theia 73), they reported \noriginal\ candidate members.  We
matched these stars against the latest Gaia EDR3 observations using
the \texttt{dr2\_neighbourhood} table from the ESA archive,\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GEDR3/Gaia_archive/chap_datamodel/sec_dm_auxiliary_tables/ssec_dm_dr2_neighbourhood.html}.}
and took the closest proper motion and epoch-corrected angular
distance as the presumed match
\citep{gaia_collaboration_2021_edr3}.  In Figure~\ref{fig:XYZvtang},
have shown galactic positions only for the stars with
parallax signal-to-noise exceeding 20.  The reported cluster members
(gray and black points) extend over a much larger volume than the
cluster previously identified by \citet{stephenson_possible_1959} and
later corroborated by \citet{eggen_photometric_1968}.  While the
non-uniform ``clumps'' of stars might comprise a {\it bona fide}
cluster of identically-aged stars, they could also be heavily
contaminated by field stars.  We therefore considered stars only in
the immediate kinematic and spatial vicinity of \sn\ as candidate
cluster members.  We performed the selection cuts manually, by
drawing lassos with the interactive \texttt{glue} visualization tool
\citep{beaumont_2014_13866} in the four projections shown in
Figure~\ref{fig:XYZvtang}.  The overlap between the Kepler
field and the resulting candidate cluster members is shown in
Figure~\ref{fig:skychart}.  While this method will
include some field interlopers in the ``cluster star'' sample, and
vice-versa, it should suffice for our aim of verifying the existence
of the cluster in the vicinity of \sn.

@@

% Randich+18: 43.7 +4.3 - 3.9 LDB, for E(B-V) = 0.068 +/- 0.025
% Dobbie+10: 46 +6 -5 LDB, for

@@

\subsection{Kepler\,1627A}
\subsubsection{Age}
Based on the spatial and kinematic association of \sn\ with the \cn,
and the assumption that the planet formed shortly after the star, it
seems likely that \sn\ is the same age as the cluster. There are
two consistency checks on whether this is true: rotation and lithium.  Based on the Kepler
light curve, the rotation period is $2.642\pm0.042$\,days, where the
quoted uncertainty is based on the scatter in rotation periods
measured from each individual Kepler quarter.  This is consistent with
comparable cluster members (Figure~\ref{fig:age}).

To infer the abundance of Li\,\textsc{I} from the 6708\,\AA\ doublet
\citep[{\it e.g.},][]{soderblom_ages_2014}, we acquired an iodine-free
spectrum from Keck/HIRES on the night of 2021 March 26 using the
standard setup and reduction techniques of the California Planet
Survey \citep{howard_cps_2010}.  Following the equivalent width
measurement procedure described by \citet{bouma_2021_ngc2516}, we find
${\rm EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   This value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Nonetheless,
given the stellar effective temperature (Table~\ref{tab:starparams}),
this measurement is in agreement with expectations for a
$\approx40$\,Myr star ({\it e.g.}, as measured in IC~2602 by
\citealt{randich_gaiaeso_2018}).  It is also larger than any lithium
equivalent widths measured by \citet{berger_identifying_2018} in their
analysis of 1{,}301 Kepler-star spectra.

@@

Figure~\ref{fig:kep1627binary} summarizes the results of the
high-resolution imaging.  The Gaia EDR3 parallax for the primary
implies a projected separation of $53 \pm 4$\,AU, assuming the
companion is bound.  Although the companion is unresolved in the Gaia
source catalog (there are no comoving, codistant candidate companions
brighter than $G < 20.5$ mag within $\rho < 120\arcsec$), its
existence was also suggested by the primary star's large renormalized unit weight error (RUWE),
relative to other members of the \cn.  Based on the apparent
separation, the binary orbital period is of order hundreds of years.
The large RUWE is therefore more likely to be caused by a PSF-mismatch
skewing the Gaia centroiding during successive scans, rather than true
astrometric motion.  Regardless, given the low geometric probability that a companion imaged at
$\rho \approx 0\farcs16$ is a chance line-of-sight companion, we
proceed under the assumption that the companion is bound, and that
Kepler\,1627 is a binary.  
Given the distance and age, the models of
\citet{baraffe_new_2015} imply a companion mass of $M_{\rm B} \approx
0.33 M_{\odot}$ and companion temperature of $T_{\rm eff,B} \approx
3450$ K.  The corresponding spectral type is roughly M2.5V
\citep{pecaut_mamajek_2013}.
% \footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}, version \texttt{2021/03/02}.}
These models combined with the NIRC2 contrast limits imply
physical limits on tertiary companions of $M_{\rm ter} < 50
M_{\rm Jup}$ at $\rho = 50$\,AU, $M_{\rm ter} < 20 M_{\rm Jup}$ at $\rho =
100$\,AU, and $M_{\rm ter} < 10 M_{\rm Jup}$ at $\rho = 330$\,AU.

@@

The Kepler space telescope observed \sn\ at a 30-minute cadence from
2009 May 2 until 2013 April 8.  Data gaps during quarters 4, 9, and 13
led to an average duty cycle over the 3.9~year interval of 78\%.  \sn\
was also observed at 1-minute cadence from 2012 Oct 5 until 2013 Jan
11.  The top panel of Figure~\ref{fig:lc} shows a portion of the 30-minute
cadence \texttt{PDCSAP} light curve.  Nonastrophysical variability has
been removed using the methods discussed by
\citet{smith_kepler_PDC_2017}; the default optimal aperture was
assumed \citep{smith_finding_2016}. 
Cadences with non-zero quality flags (9\% of the data) have been omitted.
 The resulting photometry is dominated by
a quasi-periodic starspot signal with a peak-to-peak amplitude that
varies between 2\% and 8\%.  
Previous analyses have identified and
characterized the smaller transit signal
\citep{2012ApJS..199...24T,thompson_planetary_2018}, validated its
planetary nature \citep{morton_false_2016}, and even searched the
system for transit timing variations \citep{holczer_transit_2016}.
Nonetheless, since the cluster membership provides us
with more precise stellar parameters than those previously available,
we opted to reanalyze the
light curve.

@@

Figure~\ref{fig:lc} shows the resulting best-fit model in orange (top) and
purple (bottom).
The model parameters and their uncertainties, given in Table~\ref{tab:posterior}, are
broadly consistent with a mini-Neptune sized planet ($3.82\pm0.16\,R_\oplus$) on a close-in circular\footnote{ Our transit fitting
	yields $e<0.48$ at 2-$\sigma$; the constraints on the eccentricity are
	not particularly strong.} orbit around a G8V host star ($0.88 \pm 0.02
R_\odot$).  This best-fit planet size is consistent with those
previously reported by \citet{morton_false_2016} and
\citet{berger_identifying_2018}, and corrects for the small
amount of flux dilution from Kepler\,1627B.
%at 0.3-$\sigma$ and 0.2-$\sigma$ respectively.

@@

To determine whether the asymmetry is a systematic caused by our stellar variability model,
we explored an alternative
approach in which we isolated each transit window and locally fitted
out polynomial trends, and then binned all the observed transits; the
asymmetry was still present at a comparable amplitude.  
Appendix~\ref{app:asymmetry} includes a deeper analysis, and
finds that the asymmetry also seems to be robust to different methods of
data binning in time and by local light curve slope.  The most likely
astrophysical explanations are discussed in Section~\ref{sec:conc}.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
		The time of each Kepler transit was measured, along with the local
		slope of the light curve.  The two quantities appear
		anti-correlated, which is most easily explained by starspot
		crossings during the first (second) half of transit inducing a
		positive (negative) TTV, provided that the orbit is prograde
		\citep{mazeh_time_2015}.  The units along the abscissa can
		be understood by considering that the stellar flux changes by
		$\sim$60\,ppt per half rotation period ($\sim$1.3\,days).
		\label{fig:corr}
	}
\end{figure}

% rotation period from plot_rotation_period_windowslider.py

@@

% (0.7-2.0\% V-band to G-band dmag difference from EEM table; NOTE
% could determine using model spectra)
As an initial plausibility check,
Kepler\,1627B contributes 1\% to 2\% of the total flux observed in
the Kepler aperture.  
For the sake of argument, assume the former value.
The observed transit has a depth of $\approx$0.18\%.  A
18\% deep eclipse of the secondary star would therefore be needed to
produce a signal with the appropriate depth.  The shape of the
transit signal however requires the impact parameter to be below 0.77
(2-$\sigma$); the tertiary transiting the secondary would
therefore need to be non-grazing with $R_3/R_2 \approx 0.4$.
%Assuming a $\approx 0.46R_\odot$ radius of the imaged secondary
%from the \citet{baraffe_new_2015} models, this
%would imply a tertiary stellar radius of $\approx 0.2R_\odot$.
This
yields a contradiction:  this scenario would require an ingress and
egress phase that each span $\approx$40\% of the transit duration
($\approx 68\,{\rm minutes}$).  The actual measured ingress and egress
duration is $\approx 17\,{\rm minutes}$, a factor of four times too
short.  The combination of Kepler 1627B's brightness, the transit
depth, and the ingress duration therefore disfavor the scenario that
Kepler 1627B might host the transit signal.

% Baraffe+15: M_B 0.33 Mdot
% Rstar = 0.455 --> 0.465 Rsun
%

% At 30 Myr, a 0.44\,$M_\odot$ solar-metallicity dwarf is $\approx 26\%$
% larger than when it is fully contracted on the main sequence
% (0.40\,$R_\odot$ vs{.} 0.50\,$R_\odot$; ).

There are two other new lines of evidence that confirm the planetary
interpretation.  First, the transit duration and the orbital period
are inconsistent with an eclipsing body around the M-dwarf companion:
we find $\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for the companion is $\approx 4.6\,{\rm
g\,cm}^{-3}$ (Table~\ref{tab:posterior}; \citealt{choi_mesa_2016}).
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.
While the planet might hypothetically still orbit a hidden close and
bright companion, such scenarios are ruled out by {\it i)} a lack of
secondary lines in the HIRES spectra and {\it ii)} a lack of
secondary rotation signals in the Kepler photometry.

%NOTE to the arxiv readers:, the $\approx$100 days of short-cadence
%Kepler observations also mitigate the cadence-induced smearing, and
%enable a more precise measurement of the transit impact parameter
%\citep{kipping_binning_2010}.  The planet transits with $b<0.YY$
%(2-$\sigma$) from the 1-minute data, compared to $<0.76$ (2-$\sigma$)
%from the 30-minute data.  This implies an even stronger constraint on
%the transit shape in an analysis of the false positive probability.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radial velocities acquired using Keck/HIRES during the transit of
			2021 Aug 7, observed simultaneously with MuSCAT3.}  Shaded bands
		show 2-$\sigma$ model uncertainties.  The photometric transit
		depths are consistent across the {\it griz} bandpasses.  The
		best-fitting model in the top panel includes the RM effect and a quadratic trend
		in time to model the spot-induced $\approx$\,$250$\ms\ trend (see Appendix~\ref{app:rm}).  The radial velocity jitter
		over the 15~minute exposure timescale ($\sigma_{\rm RV}\approx30$\ms) prevented us from detecting the RM
		effect.
		The RV variations are strongly correlated with varying emission in the Ca H and K lines (middle panel).
		\label{fig:ground}
	}
\end{figure}

A third supporting line of evidence for the planetary interpretation
exists, though we consider it less definitive than the stellar
density and TTV-local slope correlation.  We observed a transit of
\pn\ on the night of 2021 Aug 7 simultaneously with Keck/HIRES and
MuSCAT3.  We scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show the transit (Figure~\ref{fig:ground}).  Fitting
the MuSCAT3 photometry with a model that lets the transit depths vary
across each bandpass, we find {\it griz} depths consistent with the
Kepler depth at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  The
MuSCAT3 observations also suggest a transit duration $17.4\pm3.6\ {\rm
minutes}$ shorter than the Kepler transits; further photometric
follow-up could help confirm whether the transit duration is indeed
changing.  For our RM analysis, the details are discussed in
Appendix~\ref{app:rm}.  While the velocities are marginally more
consistent with a prograde or polar orbit than a retrograde orbit, the
spot-corrected exposure-to-exposure scatter ($\sigma_{\rm RV}\approx
30$\ms) is comparable to the expected velocity anomaly assuming an
aligned orbit ($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$).  We
are therefore not in a position to claim a spectroscopic detection of
the RM effect, nor to quantify the stellar obliquity.

@@

Since the transit asymmetry seems robust against most methods of
binning the data, we considered four possible astrophysical
interpretations: gravity darkening, transit timing variations,
spot-crossing events, and a persistent asymmetric dusty outflow.

>>>>

\title{
  A 38 Million Year Old Mini-Neptune in the Kepler Field
}

@@

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.8\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\,{\rm pc}$) and it resembles the Sun.  Here we show using
  Gaia kinematics, TESS stellar rotation periods, and spectroscopic
  lithium abundances that Kepler\,1627 is a member of the \clusterage\
  old $\delta$~Lyr cluster.  To our knowledge, this makes
  Kepler\,1627Ab the youngest planet with a precise age yet found by
  the main Kepler mission.  The Kepler photometry shows two
  peculiarities: the average transit profile is asymmetric, and the
  individual transit times are correlated with the local light curve
  slope.  We discuss possible explanations for each anomaly.  More
  broadly, the $\delta$~Lyr cluster
  is one of $\sim$10$^3$ coeval groups whose properties have been clarified
  by Gaia.  Many other exoplanet hosts are potentially kinematic members
  of these clusters; their candidate memberships can be verified by
  measuring stellar rotation periods in the TESS full frame images.
\end{abstract}

@@

For instance, the ``mini-Neptunes'', thought to be made of metal
cores, silicate mantles \citep{kite_atmosphere_2020}, and extended
hydrogen-dominated atmospheres, are expected to shrink
in size by factors of several over their first $10^8$ years.
Specifically, in the models of \citet{owen_atmospheres_2016} and
\citet{owen_constraining_2020}, the $\approx5\,M_\oplus$ planets start
with sizes of 4--12\,$R_\oplus$ shortly after the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2--4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years after the disk
disperses \citep{ikoma_situ_2012}, stellar
irradiation and internal heat can also power gradual outflows
which, if strong enough, can deplete or entirely strip the atmospheric
envelope \citep{Owen_Wu_2013,ginzburg_corepowered_2018}.
Discovering young planets, measuring their masses, and detecting their
atmospheric outflows are key steps toward testing this paradigm, which
is often invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017}.

@@

Matching our young star list against stars observed by Kepler revealed
that Kepler observed a portion of the \cn\ (Stephenson-1; Theia~73).
More specifically, a clustering analysis of the Gaia data by
\citet{KounkelCovey2019} reported that Kepler~1627 (KIC 6184894; KOI
5245; TIC 120105470) is a \cn\ member.  Given the previous statistical
validation of the close-in mini-Neptune Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by examining the properties of the cluster
(Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr cluster is
\clusterage\ old, and in Section~\ref{sec:stars} show that \sn\ is
both a binary and also a member of the cluster.  Focusing on the
planet (Section~\ref{sec:planet}), we confirm that despite the
existence of the previously unreported M2.5V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.
Based on a correlation between the planetary transit times and the
local light curve slope, the orbit may also be prograde.  We conclude
by highlighting broader implications for our ability to age-date a
larger sample of planets (Section~\ref{sec:conc}).

@@

\citet{KounkelCovey2019} applied an unsupervised clustering algorithm
to Gaia DR2 on-sky positions, proper motions, and parallaxes for stars
within the nearest kiloparsec.  For the \cn\ (Theia 73), they reported
\noriginal\ candidate members.  We matched these stars against the
latest Gaia EDR3 observations using the \texttt{dr2\_neighbourhood}
table from the ESA archive,\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GEDR3/Gaia_archive/chap_datamodel/sec_dm_auxiliary_tables/ssec_dm_dr2_neighbourhood.html}.}
taking the stars closest in proper motion and epoch-corrected angular
distance as the presumed match \citep{gaia_collaboration_2021_edr3}.
In Figure~\ref{fig:XYZvtang}, have shown galactic positions only for
the stars with parallax signal-to-noise exceeding 20.  The reported
cluster members (gray and black points) extend over a much larger
volume than the cluster previously identified by
\citet{stephenson_possible_1959} and later corroborated by
\citet{eggen_photometric_1968}.  While the non-uniform ``clumps'' of
stars might comprise a {\it bona fide} cluster of identically-aged
stars, they could also be heavily contaminated by field stars.  We
therefore considered stars only in the immediate kinematic and spatial
vicinity of \sn\ as candidate cluster members.  We performed the
selection cuts manually, by drawing lassos with the interactive
\texttt{glue} visualization tool \citep{beaumont_2014_13866} in the
four projections shown in Figure~\ref{fig:XYZvtang}.  The overlap
between the Kepler field and the resulting candidate cluster members
is shown in Figure~\ref{fig:skychart}.  While this method will include
some field interlopers in the ``cluster star'' sample, and vice-versa,
it should suffice for our aim of verifying the existence of the
cluster in the vicinity of \sn.

@@

% Randich+18: 43.7 +4.3 - 3.9 LDB
% Dobbie+10: 46 +6 -5 LDB

@@

\subsection{Kepler\,1627A}
\subsubsection{Age}
% rotation period from plot_rotation_period_windowslider.py
Based on the spatial and kinematic association of \sn\ with the \cn,
and the assumption that the planet formed shortly after the star, it
seems likely that \sn\ is the same age as the cluster. There are two
consistency checks on whether this is true: rotation and lithium.
Based on the Kepler light curve, the rotation period is
$2.642\pm0.042$\,days, where the quoted uncertainty is based on the
scatter in rotation periods measured from each individual Kepler
quarter.  This is consistent with comparable cluster members
(Figure~\ref{fig:age}).

To infer the amount of Li\,\textsc{I} from the 6708\,\AA\ doublet
\citep[{\it e.g.},][]{soderblom_ages_2014}, we acquired an iodine-free
spectrum from Keck/HIRES on the night of 2021 March 26 using the
standard setup and reduction techniques of the California Planet
Survey \citep{howard_cps_2010}.  Following the equivalent width
measurement procedure described by \citet{bouma_2021_ngc2516}, we find
${\rm EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   This value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Nonetheless,
given the stellar effective temperature (Table~\ref{tab:starparams}),
this measurement is in agreement with expectations for a
$\approx40$\,Myr star ({\it e.g.}, as measured in IC~2602 by
\citealt{randich_gaiaeso_2018}).  It is also larger than any lithium
equivalent widths measured by \citet{berger_identifying_2018} in their
analysis of 1{,}301 Kepler-star spectra.

@@

% \footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}, version \texttt{2021/03/02}.}
Figure~\ref{fig:kep1627binary} summarizes the results of the
high-resolution imaging.  The Gaia EDR3 parallax for the primary
implies a projected separation of $53 \pm 4$\,AU, assuming the
companion is bound.  Although the companion is unresolved in the Gaia
source catalog (there are no comoving, codistant candidate companions
brighter than $G < 20.5$ mag within $\rho < 120\arcsec$), its
existence was also suggested by the primary star's large renormalized
unit weight error (RUWE), relative to other members of the \cn.  Based
on the apparent separation, the binary orbital period is of order
hundreds of years.  The large RUWE is therefore more likely to be
caused by a PSF-mismatch skewing the Gaia centroiding during
successive scans, rather than true astrometric motion.  Regardless,
given the low geometric probability that a companion imaged at $\rho
\approx 0\farcs16$ is a chance line-of-sight companion, we proceed
under the assumption that the companion is bound, and that
Kepler\,1627 is a binary.  Given the distance and age, the models of
\citet{baraffe_new_2015} imply a companion mass of $M_{\rm B} \approx
0.33 M_{\odot}$ and companion temperature of $T_{\rm eff,B} \approx
3450$ K.  The corresponding spectral type is roughly M2.5V
\citep{pecaut_mamajek_2013}.  These models combined with the NIRC2
contrast limits imply physical limits on tertiary companions of
$M_{\rm ter} < 50 M_{\rm Jup}$ at $\rho = 50$\,AU, $M_{\rm ter} < 20
M_{\rm Jup}$ at $\rho = 100$\,AU, and $M_{\rm ter} < 10 M_{\rm Jup}$
at $\rho = 330$\,AU.

@@

The Kepler space telescope observed \sn\ at a 30-minute cadence from
2009 May 2 until 2013 April 8.  Data gaps during quarters 4, 9, and 13
led to an average duty cycle over the 3.9~year interval of 67\%.  \sn\
was also observed at 1-minute cadence from 2012 Oct 5 until 2013 Jan
11.  The top panel of Figure~\ref{fig:lc} shows a portion of the
30-minute cadence \texttt{PDCSAP} light curve.  Nonastrophysical
variability has been removed using the methods discussed by
\citet{smith_kepler_PDC_2017}; the default optimal aperture was
assumed \citep{smith_finding_2016}.  Cadences with non-zero quality
flags (9\% of the data) have been omitted.  The resulting photometry
is dominated by a quasi-periodic starspot signal with a peak-to-peak
amplitude that varies between 2\% and 8\%.  Previous analyses have
identified and characterized the smaller transit signal
\citep{2012ApJS..199...24T,thompson_planetary_2018}, validated its
planetary nature \citep{morton_false_2016}, and even searched the
system for transit timing variations \citep{holczer_transit_2016}.
Nonetheless, since the cluster membership provides us with more
precise stellar parameters than those previously available, we opted
to reanalyze the light curve.

@@

Figure~\ref{fig:lc} shows the resulting best-fit model in orange (top)
and purple (bottom).  The model parameters and their uncertainties,
given in Table~\ref{tab:posterior}, are broadly consistent with a
mini-Neptune sized planet ($3.82\pm0.16\,R_\oplus$) on a close-in
circular\footnote{ Our transit fitting yields $e<0.48$ at 2-$\sigma$;
the constraints on the eccentricity are not particularly strong.}
orbit around a G8V host star ($0.88 \pm 0.02 R_\odot$).  This best-fit
planet size is consistent with those previously reported by
\citet{morton_false_2016} and \citet{berger_identifying_2018}, and
corrects for the small amount of flux dilution from Kepler\,1627B.

@@

To determine whether the asymmetry is a systematic caused by our
stellar variability model, we explored an alternative approach in
which we isolated each transit window and locally fitted out
polynomial trends, and then binned all the observed transits; the
asymmetry was still present at a comparable amplitude.
Appendix~\ref{app:asymmetry} includes a deeper analysis, and finds
that the asymmetry also seems to be robust to different methods of
data binning in time and by local light curve slope.  Possible
astrophysical explanations are discussed in Section~\ref{sec:conc}.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Evidence for a prograde orbit of Kepler 1627 Ab.} The time of
    each Kepler transit was measured, along with the local slope of
    the light curve.  The two quantities appear anti-correlated, which
    is most easily explained by starspot crossings during the first
    (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa can be understood by considering that the
    stellar flux changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
		\label{fig:corr}
	}
\end{figure}

@@

% (0.7-2.0\% V-band to G-band dmag difference from EEM table)

As an initial plausibility check, Kepler\,1627B contributes 1\% to 2\%
of the total flux observed in the Kepler aperture.  For the sake of
argument, assume the former value.  The observed transit has a depth
of $\approx$0.18\%.  A 18\% deep eclipse of Kepler\,1627B would
therefore be needed to produce a signal with the appropriate depth.
The shape of the transit signal however requires the impact parameter
to be below 0.77 (2-$\sigma$); the tertiary transiting the secondary
would therefore need to be non-grazing with $R_3/R_2 \approx 0.4$.
This yields a contradiction:  this scenario would require an ingress
and egress phase that each span $\approx$40\% of the transit duration
($\approx 68\,{\rm minutes}$).  The actual measured ingress and egress
duration is $\approx 17\,{\rm minutes}$, a factor of four times too
short.  The combination of Kepler 1627B's brightness, the transit
depth, and the ingress duration therefore disfavor the scenario that
Kepler 1627B might host the transit signal.

% Baraffe+15: M_B 0.33 Mdot
% Rstar = 0.455 --> 0.465 Rsun

There are two other new lines of evidence that confirm the planetary
interpretation.  First, the stellar density implied by the transit duration and orbital period
is inconsistent with an eclipsing body around the M-dwarf companion:
we find $\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for Kepler\,1627B is $\approx 4.6\,{\rm
g\,cm}^{-3}$ (Table~\ref{tab:posterior}; \citealt{choi_mesa_2016}).
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.  While the planet
might hypothetically still orbit a hidden close and bright companion,
this possibility is ruled out by {\it i)} a lack of secondary lines in
the HIRES spectra and {\it ii)} a lack of secondary rotation signals
in the Kepler photometry.

%NOTE to the arxiv readers:, the $\approx$100 days of short-cadence
%Kepler observations also mitigate the cadence-induced smearing, and
%enable a more precise measurement of the transit impact parameter.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Radial velocities acquired using Keck/HIRES during the
    transit of 2021 Aug 7, observed simultaneously with MuSCAT3.}
    Shaded bands show 2-$\sigma$ model uncertainties.  The photometric
    transit depths are consistent across the {\it griz} bandpasses.
    The best-fitting model in the top panel includes the RM effect and
    a quadratic trend in time to model the spot-induced
    $\approx$\,$250$\ms\ trend (see Appendix~\ref{app:rm}).  The
    radial velocity jitter over the 15~minute exposure timescale
    ($\sigma_{\rm RV}\approx30$\ms) prevented us from detecting the RM
    effect.  The RV variations are strongly correlated with varying
    emission in the Ca H and K lines (middle panel).
		\label{fig:ground}
	}
\end{figure}

A third supporting line of evidence for the planetary interpretation
exists, though we consider it less definitive than the stellar density
and TTV-local slope correlation.  We observed a transit of \pn\ on the
night of 2021 Aug 7 simultaneously with Keck/HIRES and MuSCAT3.  We
scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show the transit (Figure~\ref{fig:ground}).  Fitting the MuSCAT3
photometry with a model that lets the transit depths vary across each
bandpass, we find {\it griz} depths consistent with the Kepler depth
at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  Conditioned on the
Kepler ephemeris and transit depth, the MuSCAT3 observations may also
show a transit duration $17.3\pm4.0\ {\rm minutes}$ shorter than the
Kepler transits; further photometric follow-up would help confirm
whether the transit duration is indeed changing.  For our RM analysis,
the details are discussed in Appendix~\ref{app:rm}.  While the
velocities are marginally more consistent with a prograde or polar
orbit than a retrograde orbit, the spot-corrected exposure-to-exposure
scatter ($\sigma_{\rm RV}\approx 30$\ms) is comparable to the expected
RM anomaly assuming an aligned orbit ($\Delta v_{\rm RM}\approx
20\,{\rm m\,s}^{-1}$).  We are therefore not in a position to claim a
spectroscopic detection of the RM effect, nor to quantify the stellar
obliquity.

@@

The transit asymmetry seems robust against most methods of binning the
data, though with some caveats ({\it e.g.}, the ``middle quartile'' in
local flux (${\rm d}f/{\rm d}t\in[0.001,0.033]\,{\rm ppt\,day}^{-1}$),
where the asymmetry does not appear).  Nonetheless, if the effect were
entirely systematic we would expect to see it change as a function of
the sign of the local slope or TTV.  We therefore considered four
possible astrophysical interpretations: gravity darkening, transit
timing variations, spot-crossing events, and a persistent asymmetric
dusty outflow.
